\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-01-16 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
GMinT tidied up

\section{Bias in forecast reconciliation}\label{sec:BiasInRecon}

>>>>

{\color{blue}

\subsection{Generalised MinT}

As discussed in the previous section, the MinT method has a motivation that is quite separate from the considerations of Theorem~\ref{th:gdistred}.  In spite of this, it is also true that Theorem~\ref{th:gdistred} guarantees that MinT will always improve upon base forecasts when the loss function is based on the norm $\|.\|_{\bm{\Sigma}^{-1}}$.  This will be verified in our empirical example in Section~\ref{sec:EmpStudy}.  For this reason there is the potential to conflate the choice of loss function, with the desire to attain the attractive statistical properties of trace minimisation.  We not propose a generalisation of the MinT method that uncouples these two ideas.

Consider a loss function given based on $\|.\|_{\bm{W}^{-1}}$ where the choice of $\bm{W}$ is determined by the context of the forecasting problem rather than by statistical considerations.  For instance, our empirical example in Section~\ref{sec:EmpStudy} considers the number of tourists visiting different regions in Australia. Here, a sensible loss function may weight tourist numbers by the average spend of tourists in each region.  Theorem~\ref{th:gdistred} suggests a reconciliation that is guaranteed to improve base forecasts with respect to the loss function based on $\bm{W}$.  This is an orthogonal projection in the space transformed by pre-multiplication by $W^{-1/2}$.

In the case where $\bm{W}=\bm{I}$, it has been established that MinT often outperform OLS.  Therefore we propose a generalisation of MinT that accounts for user-defined loss functions.  Rather than minimising the trace of the variance covariance matrix of forecast errors, the aim is to minimise the trace of the variance covariance matrix of the \textit{transformed} forecast errors. The projection that minimises the trace of variance covariance matrix of ${\bm W}^{-1/2}{y-\hat{\bm y}}$ is $\bm{S}\bm{G}^{\text{GMinT}}$, where
\begin{equation*}
\bm{G}^{\text{GMinT}}=\left(\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\bm{S}\right)^{-1}\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\,.
\end{equation*} 
To the best of our knowledge, this method, which we call generalised MinT has not been proposed so far in the literature.  The key advantage of Generalised MinT allows the choice of loss function to be decoupled from the choice of an oblique projection with attractive statistical properties.

}
\section{Bias in forecast reconciliation}\label{sec:BiasInRecon}
